Dissertation Proposal

### 2023-11-07 proposal.tex
sec 7.1, 7.2

@@

\section{Generating and Collating Problems}
\label{s:gen-prob-quizius}

Additionally, in this paper, we intentionally use the word
mis\emph{conceptions} rather than mis\emph{take}. A mistake can happen
for any reason (e.g., selecting the wrong answer from a menu). A
misconception, however, implies a conceptual problem: the student has
formed an incorrect concept in their head. For instance, they may
think that mutable structures are copied on function calls, or that
scope is resolved dynamically. This requires probing what they are
thinking.

Finally, we are inspired by the significant body of education research
on \emph{concept inventories} \citep{hestenesForceConceptInventory1992} (with a growing
number for computer science, as a survey lists \citep{taylorComputerScienceConcept2014}). In
terms of mechanics, a concept inventory is just an instrument
consisting of multiple-choice questions (MCQs), where each question has
one correct answer and several wrong ones. However, the wrong ones are
chosen with great care. Each one has been validated so that if a
student picks it, we can quite unambiguously determine \emph{what
  misconception the student has}. For instance, if the question is
``What is \lstinline|sqrt(4)|?'', then \lstinline|37| is probably an
uninteresting wrong answer, but if people appear to confuse
square-roots with squares, then \lstinline|16| would be present as an
answer.\footnote{Concept inventories are thus useful in many
  settings. For instance, an educator can use them with clickers to
  get quick feedback from a class. If several students pick a
  specific wrong answer, the educator not only knows they are wrong,
  but also has a strong inkling of \emph{precisely what} misconception
  that group has and can address it directly. I expect our
  instruments to be useful in the same way.}

All these, however, add up to a somewhat challenging demand. I want
to produce a list of questions (each one an MCQ) such that
\begin{enumerate}

  \item we can get past the expert blind spot,

  \item we have a sense of what misconceptions students have, and

  \item we can generally associate wrong answers with specific
        misconceptions, approaching a concept inventory.

@@

Our main solution to the expert blind spot is to use the Quizius system
\citep{saarinenHarnessingWisdomClasses2019}. In contrast to the very
heavyweight process (involving a lot of expert time)
that is generally
used to create a concept inventory, Quizius uses a lightweight,
interactive approach to obtain fairly comparable data, which an expert
can then shape into a quality instrument.

In Quizius, experts create a prompt; in our case, we asked students to
create small but ``interesting'' programs using the SMoL
language. Quizius shows this prompt to students and gathers their
answers. Each student is then shown a set of programs created by other
students and asked to predict (without running it) the value produced
by the program.\footnote{In the course (\Cref{s:populations}),
  students were given credit for using Quizius but not penalized for wrong
  answers, reducing their incentive to ``cheat'' by running
  programs. They were also told that doing so would diminish the value of
  their answers. Some students seemed to do so anyway, but most
  honored the directive.} Students are also asked to provide a rationale for why
they think it will produce that output.

@@

The output from Quizius is (a) a collection of programs; (b) for
each program, a collection of predicted answers; and (c) for each
answer, a rationale. Clustering the answers is easy (after
ignoring some small syntactic differences). Thus, for
each cluster, we obtain a set of rationales.

After running Quizius in the course (\Cref{s:populations}),
we took over as experts. Determining which is the right
answer is easy. Where expert knowledge is useful is in
\emph{clustering the rationales}. If all the rationales for a wrong
answer are fairly similar, this is strong evidence that there is a
common misconception that generates it. If, however, there are
multiple rationale clusters, that means the program
is not discriminative enough to distinguish the misconceptions, and it
needs to be further refined to tell them apart. Interestingly, even
the correct answer needs to be analyzed, because sometimes correct
answers do have incorrect rationales (again, suggesting the program
needs refinement to discriminate correct conceptions
from misconceptions).

Prior work using Quizius \citep{saarinenHarnessingWisdomClasses2019} finds that students do author programs
that the experts did not imagine. In our case, we seeded Quizius with
programs from prior papers (\Cref{s:background-misconceptions}), which gives the first
few students programs to respond to. However, we found
that Quizius significantly expanded the scope of our problems and
misconceptions. In our final instrument, most programs were directly
or indirectly inspired by the output of Quizius.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{images/smol-quizzes-example.png}
  \caption{Screenshot of a SMoL Quiz question.}
  \label{f:smol-quizzes-example}
\end{figure}

@@

Having curated the output, we had to confirm that these programs were
still effective! That is, they needed to actually find student errors.

I therefore turned the programs into a set of quizzes (in the US
sense: namely, a brief test of knowledge) that we call the SMoL
Quizzes. There were three quizzes, ordered by linguistic
complexity. The first consisted of only basic operators and
first-order functions. The second added variable and structure
mutation. The third added \lstinline|lambda| and higher-order functions.

The goal of the SMoL Quizzes was to confirm that the aforementioned
processes of cleansing and enriching the problems was successful. The
quizzes were therefore administered in the third year of this project in the
same course.
\Cref{f:smol-quizzes-example} shows a
sample question. Every question got an ``Other'' option. If chosen,
the quiz gave the user a text box with the caption ``Please
specify''. The goal here was to record any other answers, which in
turn might lead to fresh misconceptions.

Question orders were partially randomized. I wanted students to get
some easy, warm-up questions initially, so those were kept at the
beginning. Similarly, we wanted programs that are syntactically
similar to stay close to each other in the quiz. This is so that, when
students got a second such program, they would not have to look far to
find the first one and confirm that they are indeed (slightly)
different, rather than wonder if they were seeing the same program
again.

Students only received feedback after having completed a whole
quiz. At the end of each quiz, they received both summative feedback
\emph{and} a refutation text that explained every program that
appeared in the quiz. Students were also encouraged to run the
programs, but we have little reason to believe that they did (and
certainly they asked few questions on the class forum about them).

Due to space limitations, we present the entire instrument in \supplRef{SMoL Quizzes/instrument}.
Here we focus on a few programs where student choices correspond to
misconceptions identified earlier, thereby also showing
that the curated programs are
still effective.
Syntactically, \lstinline|#t| and \lstinline|#f| are true and false,
while \lstinline|#(...)| is a vector. I use a * to indicate the correct
answer (which also matches the implementation's output).

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l X}
    \textbf{Questions}                       &
    \textbf{Table of Answers}                    \\\hline
    \lstinputlisting{programs/def_twice.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          $^\dag$59\% & \lstinline|2 0|             \\
          *32\%       & \lstinline|Error|           \\
          4\%         & \lstinline|Other: 2 2|      \\
          3\%         & ``Nothing is printed'' \\
          2\%         & \lstinline|0 0|             \\
        \end{tabularx}
    }                                            \\\hline
    \lstinputlisting{programs/dyn_scope.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          *65\%       & \lstinline|Error| \\
          $^\dag$29\% & \lstinline|42 #t| \\
          6\%         & Other        \\
        \end{tabularx}
    }                                            \\\hline
    \lstinputlisting{programs/reassign.txt}  & {
        \begin{tabularx}{\linewidth}{r X}
          *53\%       & \lstinline|#(6 5) 5|                 \\
          *20\%       & \lstinline|Error|                    \\
          $^\dag$11\% & \lstinline|#(6 6) 5|                 \\
          $^\dag$11\% & \lstinline|#(6 6) 6|                 \\
          5\%         & ``Nothing is printed'' or Other \\
        \end{tabularx}
    }                                            \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizFun. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-fun}
\end{table}
\Cref{t:quizzes-data-fun} lists programs in \quizFun{} that we
consider the most interesting. These data confirm the presence of
scope-related misconceptions:
\begin{enumerate}
  \item At least 59\% of students incorrectly believe that a
        variable can be defined twice in one block.
  \item 29\% of students believe that a variable defined in a function
        will be available in the top-level (or global) environment
        after the function is called. That is, these students may have a
        dynamic scope misconception.
  \item 22\% (11\% + 11\%) of students believe variables themselves
        can be passed as arguments and redefined inside the function.
        They disagree on whether the redefinition persists after the
        function call.
\end{enumerate}

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l X}
    \textbf{Question}                           &
    \textbf{Table of Answers}                       \\\hline
    \lstinputlisting{programs/circularity.txt}  & {
        \begin{tabularx}{\linewidth}{r X}
          $^\dag$50\% & \lstinline|#(#(2 #(2 3)) #(2 3))| \\
          *29\%       & \lstinline|x=#(x x)| or
          something similar. Both \lstinline|(left x)| and \lstinline|(right x)|
          are \lstinline|x| itself.                       \\
          $^\dag$16\% & \lstinline|Error|                 \\
          5\%         & Other                        \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/mvec_in_mvec.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          *62\%       & \lstinline|#(#(100 2 3 4) #(100 2 3 4))| \\
          $^\dag$26\% & \lstinline|#(#(1 2 3 4) #(100 2 3 4))|   \\
          6\%         & \texttt{Error}                      \\
          4\%         & \lstinline|#(#(1 2 3 4) #(1 2 3 4))|     \\
          2\%         & Other                               \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/vset_in_let.txt}  & {
        \begin{tabularx}{\linewidth}{r X}
          *59\%       & \lstinline|#(10)|  \\
          $^\dag$36\% & \lstinline|#(123)| \\
          5\%         & Other         \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/var_as_arg.txt}   & {
        \begin{tabularx}{\linewidth}{r X}
          *65\%       & \texttt{12} \\
          $^\dag$31\% & \texttt{0}  \\
          4\%         & Other       \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/setset.txt}       & {
        \begin{tabularx}{\linewidth}{r X}
          *59\%       & Other: \texttt{5 7}   \\
          $^\dag$27\% & \texttt{6 7}          \\
          11\%        & \texttt{5 5}          \\
          2\%         & Other: \texttt{Error} \\
          1\%         & Other: \texttt{5 6}   \\
        \end{tabularx}
    }                                               \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizState. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-state}
\end{table}
\Cref{t:quizzes-data-state} lists interesting programs after the
addition of state. These data suggest the students have aliasing-related misconceptions:
\begin{itemize}
  \item Up to 50\% of students think vectors are copied rather than
        aliased.
  \item 16\% of students think trying to construct and print a
        self-referring vector would error. (This program is ambiguous:
        \emph{constructing} works in most SMoL languages, but \emph{printing}
        may well cause a problem. These identified ambiguities are
        addressed in \Cref{s:tutor-refine-program-set}.)
  \item 31\% of students think a variable is aliased by a parameter if
        the two variables have the same name. Perhaps interestingly,
        fewer students (27\%) think the variable aliasing would
        happen if the two variables had different names.
\end{itemize}

@@

% This quiz includes two groups of questions. Each group contains
% programs that are really similar to each other. The order of the two
% groups and the other questions are randomized. Question order within
% each group is also randomized. The first two programs in the
% \Cref{t:quizzes-data-hof} belongs to one group, which is about
% changing a function's behavior by mutating a variable defined outside
% the function. The other group is about equality between functions. The
% latter group is not included in the main text because we think it is
% not very related to the theme of this paper.

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l X}
    \textbf{Question}                                 &
    \textbf{Table of Answers}                             \\\hline
    \lstinputlisting{programs/fun_returns_lambda.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          *82\%       & \lstinline|3|     \\
          $^\dag$17\% & \lstinline|Error| \\
          1\%         & Other        \\
        \end{tabularx}
    }                                                     \\\hline
    \lstinputlisting{programs/fun_and_state_1.txt}    & {
        \begin{tabularx}{\linewidth}{r X}
          *74\%       & \lstinline|4|            \\
          $^\dag$21\% & \lstinline|3|            \\
          6\%         & Other: \lstinline|Error| \\
        \end{tabularx}
    }                                                     \\\hline
    \lstinputlisting{programs/fun_and_state_2.txt}    & {
        \begin{tabularx}{\linewidth}{r X}
          *88\%       & \lstinline|4|            \\
          $^\dag$10\% & \lstinline|3|            \\
          3\%         & Other: \lstinline|Error| \\
        \end{tabularx}
    }                                                     \\\hline
    \lstinputlisting{programs/counter.txt}            & {
        \begin{tabularx}{\linewidth}{r X}
          *62\%       & \lstinline|1 1 2 3 2| \\
          $^\dag$34\% & \lstinline|1 1 1 1 1| \\
          4\%         & Other            \\
          1\%         & \lstinline|1 1 2 3 4| \\
        \end{tabularx}
    }                                                     \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizHof. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-hof}
\end{table}
\Cref{t:quizzes-data-hof} lists interesting programs
after the addition of closures and higher-order functions.
It extends what we saw with loops in
\Cref{s:intro}: that students have misconceptions about their interaction with mutable variables:
\begin{itemize}
  \item 17\% of students think \texttt{lambda} functions can't refer
        to free variables.
  \item 21\% of the students think mutating a variable defined outside
        a lambda can't possibly change the behavior of the lambda.
        Perhaps interestingly, this
        misconception seems to depend on how the lambda is constructed
        (compare the middle two programs).
  \item Student understanding of the
        \lstinline|let|-over-\lstinline|lambda| pattern is weak.
\end{itemize}

>>>>

Known misconceptions are often detected with a kind of instruments
called \emph{concept inventories}
\citep{hestenesForceConceptInventory1992,taylorComputerScienceConcept2014}.
In terms of mechanics, a concept inventory is just an instrument
consisting of multiple-choice questions (MCQs), where each question
has one correct answer and several wrong ones. However, the wrong ones
are chosen with great care. Each one has been validated so that if a
student picks it, we can quite unambiguously determine \emph{what
misconception the student has}. For instance, if the question is
``What is \lstinline|sqrt(4)|?'', then \lstinline|37| is probably an
uninteresting wrong answer, but if people appear to confuse
square-roots with squares, then \lstinline|16| would be present as an
answer.\footnote{Concept inventories are thus useful in many settings.
For instance, an educator can use them with clickers to get quick
feedback from a class. If several students pick a specific wrong
answer, the educator not only knows they are wrong, but also has a
strong inkling of \emph{precisely what} misconception that group has
and can address it directly.}

@@

\section{Generating and Collating Problems}%
\label{s:gen-prob-quizius}

% Additionally, in this paper, we intentionally use the word
% mis\emph{conceptions} rather than mis\emph{take}. A mistake can happen
% for any reason (e.g., selecting the wrong answer from a menu). A
% misconception, however, implies a conceptual problem: the student has
% formed an incorrect concept in their head. For instance, they may
% think that mutable structures are copied on function calls, or that
% scope is resolved dynamically. This requires probing what they are
% thinking.

% All these, however, add up to a somewhat challenging demand. I want
% to produce a list of questions (each one an MCQ) such that
% \begin{enumerate}

%   \item we can get past the expert blind spot,

%   \item we have a sense of what misconceptions students have, and

%   \item we can generally associate wrong answers with specific
%         misconceptions, approaching a concept inventory.

This section describes preliminary results on finding misconceptions
from student-written programs (\Cref{s:quizius}) and what I have done
to distill misconception-detecting programs from student inputs
(\Cref{s:smol-quizzes,s:tutor-refine-program-set}).

@@

My main solution to the expert blind spot is to use the Quizius system
\citep{saarinenHarnessingWisdomClasses2019}. In contrast to the very
heavyweight process (involving a lot of expert time) that is generally
used to create a concept inventory, Quizius uses a lightweight,
interactive approach to obtain fairly comparable data, which an expert
can then shape into a quality instrument.

In Quizius, experts create a prompt; in our case, students were to
create small but ``interesting'' programs using the SMoL
language. Quizius shows this prompt to students and gathers their
answers. Each student is then shown a set of programs created by other
students and asked to predict (without running it) the value produced
by the program.\footnote{In the course (\Cref{s:populations}),
  students were given credit for using Quizius but not penalized for wrong
  answers, reducing their incentive to ``cheat'' by running
  programs. They were also told that doing so would diminish the value of
  their answers. Some students seemed to do so anyway, but most
  honored the directive.} Students are also asked to provide a rationale for why
they think it will produce that output.

@@

The output from Quizius is (a) a collection of programs; (b) for
each program, a collection of predicted answers; and (c) for each
answer, a rationale. Clustering the answers is easy (after
ignoring some small syntactic differences). Thus, for
each cluster, I obtain a set of rationales.

After running Quizius in the course (\Cref{s:populations}),
I took over as experts. Determining which is the right
answer is easy. Where expert knowledge is useful is in
\emph{clustering the rationales}. If all the rationales for a wrong
answer are fairly similar, this is strong evidence that there is a
common misconception that generates it. If, however, there are
multiple rationale clusters, that means the program
is not discriminative enough to distinguish the misconceptions, and it
needs to be further refined to tell them apart. Interestingly, even
the correct answer needs to be analyzed, because sometimes correct
answers do have incorrect rationales (again, suggesting the program
needs refinement to discriminate correct conceptions
from misconceptions).

Prior work using Quizius \citep{saarinenHarnessingWisdomClasses2019}
finds that students do author programs that the experts did not
imagine. In our case, I seeded Quizius with programs from prior papers
(\Cref{s:background-misconceptions}), which gives the first few
students programs to respond to. However, I found that Quizius
significantly expanded the scope of our problems and misconceptions.
In our final instrument, most programs were directly or indirectly
inspired by the output of Quizius.

The Quizius instrucment was set up by other people. I analyzed the
collected data.

@@

% \begin{figure}[t]
%   \centering
%   \includegraphics[width=\linewidth]{images/smol-quizzes-example.png}
%   \caption{Screenshot of a SMoL Quiz question.}
%   \label{f:smol-quizzes-example}
% \end{figure}

@@

Having curated the output, I had to confirm that these programs were
still effective! That is, they needed to actually find student errors.

I therefore turned the programs into a set of quizzes (in the US
sense: namely, a brief test of knowledge) that I call the SMoL
Quizzes. There were three quizzes, ordered by linguistic
complexity. The first consisted of only basic operators and
first-order functions. The second added variable and structure
mutation. The third added \lstinline|lambda| and higher-order functions.

Each quiz is a sequence of MCQs. The options are from the Quizius
data. In addition, there is an ``Other'' option. If chosen, the quiz
gave the user a text box with the caption ``Please specify''. The goal
here was to record any other answers, which in turn might lead to
fresh misconceptions.

The quizzes were administered in the third year in University 1.

Question orders were partially randomized. I wanted students to get
some easy, warm-up questions initially, so those were kept at the
beginning. Similarly, I wanted programs that are syntactically
similar to stay close to each other in the quiz. This is so that, when
students got a second such program, they would not have to look far to
find the first one and confirm that they are indeed (slightly)
different, rather than wonder if they were seeing the same program
again.

Students only received feedback after having completed a whole quiz.
At the end of each quiz, they received both summative feedback
\emph{and} a refutation text that explained every program that
appeared in the quiz. Students were also encouraged to run the
programs, but I have little reason to believe that they did (and
certainly they asked few questions on the class forum about them).

Due to space limitations, I present the entire instrument in
\supplRef{SMoL Quizzes/instrument}. Here I focus on a few programs
where student choices correspond to misconceptions identified earlier,
thereby also showing that the curated programs are still effective. I
use a * to indicate the correct answer (which also matches the
implementation's output).

% Syntactically, \lstinline|#t| and \lstinline|#f| are true and false,
% while \lstinline|#(...)| is a vector.

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l X}
    \textbf{Questions}                       &
    \textbf{Table of Answers}                    \\\hline
    \lstinputlisting{programs/def_twice.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          $^\dag$59\% & \lstinline|2 0|             \\
          *32\%       & \lstinline|Error|           \\
          4\%         & \lstinline|Other: 2 2|      \\
          3\%         & ``Nothing is printed'' \\
          2\%         & \lstinline|0 0|             \\
        \end{tabularx}
    }                                            \\\hline
    \lstinputlisting{programs/dyn_scope.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          *65\%       & \lstinline|Error| \\
          $^\dag$29\% & \lstinline|42 #t| \\
          6\%         & Other        \\
        \end{tabularx}
    }                                            \\\hline
    \lstinputlisting{programs/reassign.txt}  & {
        \begin{tabularx}{\linewidth}{r X}
          *53\%       & \lstinline|#(6 5) 5|                 \\
          *20\%       & \lstinline|Error|                    \\
          $^\dag$11\% & \lstinline|#(6 6) 5|                 \\
          $^\dag$11\% & \lstinline|#(6 6) 6|                 \\
          5\%         & ``Nothing is printed'' or Other \\
        \end{tabularx}
    }                                            \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizFun. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that I discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-fun}
\end{table}
\Cref{t:quizzes-data-fun} lists programs in \quizFun{} that I
consider the most interesting. These data confirm the presence of
scope-related misconceptions:
\begin{enumerate}
  \item At least 59\% of students incorrectly believe that a
        variable can be defined twice in one block.
  \item 29\% of students believe that a variable defined in a function
        will be available in the top-level (or global) environment
        after the function is called. That is, these students may have a
        dynamic scope misconception.
  \item 22\% (11\% + 11\%) of students believe variables themselves
        can be passed as arguments and redefined inside the function.
        They disagree on whether the redefinition persists after the
        function call.
\end{enumerate}

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l X}
    \textbf{Question}                           &
    \textbf{Table of Answers}                       \\\hline
    \lstinputlisting{programs/circularity.txt}  & {
        \begin{tabularx}{\linewidth}{r X}
          $^\dag$50\% & \lstinline|#(#(2 #(2 3)) #(2 3))| \\
          *29\%       & \lstinline|x=#(x x)| or
          something similar. Both \lstinline|(left x)| and \lstinline|(right x)|
          are \lstinline|x| itself.                       \\
          $^\dag$16\% & \lstinline|Error|                 \\
          5\%         & Other                        \\
        \end{tabularx}
    }                                               \\\hline
    % \lstinputlisting{programs/mvec_in_mvec.txt} & {
    %     \begin{tabularx}{\linewidth}{r X}
    %       *62\%       & \lstinline|#(#(100 2 3 4) #(100 2 3 4))| \\
    %       $^\dag$26\% & \lstinline|#(#(1 2 3 4) #(100 2 3 4))|   \\
    %       6\%         & \texttt{Error}                      \\
    %       4\%         & \lstinline|#(#(1 2 3 4) #(1 2 3 4))|     \\
    %       2\%         & Other                               \\
    %     \end{tabularx}
    % }                                               \\\hline
    % \lstinputlisting{programs/vset_in_let.txt}  & {
    %     \begin{tabularx}{\linewidth}{r X}
    %       *59\%       & \lstinline|#(10)|  \\
    %       $^\dag$36\% & \lstinline|#(123)| \\
    %       5\%         & Other         \\
    %     \end{tabularx}
    % }                                               \\\hline
    \lstinputlisting{programs/var_as_arg.txt}   & {
        \begin{tabularx}{\linewidth}{r X}
          *65\%       & \texttt{12} \\
          $^\dag$31\% & \texttt{0}  \\
          4\%         & Other       \\
        \end{tabularx}
    }                                               \\\hline
    \lstinputlisting{programs/setset.txt}       & {
        \begin{tabularx}{\linewidth}{r X}
          *59\%       & Other: \texttt{5 7}   \\
          $^\dag$27\% & \texttt{6 7}          \\
          11\%        & \texttt{5 5}          \\
          2\%         & Other: \texttt{Error} \\
          1\%         & Other: \texttt{5 6}   \\
        \end{tabularx}
    }                                               \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizState. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-state}
\end{table}
\Cref{t:quizzes-data-state} lists interesting programs after the
addition of state. These data suggest the students have aliasing-related misconceptions:
\begin{itemize}
  \item Up to 50\% of students think vectors are copied rather than
        aliased.
  \item 16\% of students think trying to construct and print a
        self-referring vector would error. (This program is ambiguous:
        \emph{constructing} works in most SMoL languages, but \emph{printing}
        may well cause a problem. These identified ambiguities are
        addressed in \Cref{s:tutor-refine-program-set}.)
  \item 31\% of students think a variable is aliased by a parameter if
        the two variables have the same name. Perhaps interestingly,
        fewer students (27\%) think the variable aliasing would
        happen if the two variables had different names.
\end{itemize}

@@

\begin{table}[t]
  \centering
  \begin{tabularx}{\linewidth}{l X}
    \textbf{Question}                                 &
    \textbf{Table of Answers}                             \\\hline
    \lstinputlisting{programs/fun_returns_lambda.txt} & {
        \begin{tabularx}{\linewidth}{r X}
          *82\%       & \lstinline|3|     \\
          $^\dag$17\% & \lstinline|Error| \\
          1\%         & Other        \\
        \end{tabularx}
    }                                                     \\\hline
    \lstinputlisting{programs/fun_and_state_1.txt}    & {
        \begin{tabularx}{\linewidth}{r X}
          *74\%       & \lstinline|4|            \\
          $^\dag$21\% & \lstinline|3|            \\
          6\%         & Other: \lstinline|Error| \\
        \end{tabularx}
    }                                                     \\\hline
    % \lstinputlisting{programs/fun_and_state_2.txt}    & {
    %     \begin{tabularx}{\linewidth}{r X}
    %       *88\%       & \lstinline|4|            \\
    %       $^\dag$10\% & \lstinline|3|            \\
    %       3\%         & Other: \lstinline|Error| \\
    %     \end{tabularx}
    % }                                                     \\\hline
    \lstinputlisting{programs/counter.txt}            & {
        \begin{tabularx}{\linewidth}{r X}
          *62\%       & \lstinline|1 1 2 3 2| \\
          $^\dag$34\% & \lstinline|1 1 1 1 1| \\
          4\%         & Other            \\
          1\%         & \lstinline|1 1 2 3 4| \\
        \end{tabularx}
    }                                                     \\\hline
  \end{tabularx}
  \caption{Some questions and student answers from \quizHof. Each
    table row is a program and the (relative) frequencies of
    student answers. Answers that can be considered correct are marked
    with \texttt{*}. Wrong answers that we discuss are
    marked with $^\dag$.}
  \label{t:quizzes-data-hof}
\end{table}
\Cref{t:quizzes-data-hof} lists interesting programs
after the addition of closures and higher-order functions.
It extends what we saw with loops in
\Cref{s:intro}: that students have misconceptions about their interaction with mutable variables:
\begin{itemize}
  \item 17\% of students think \texttt{lambda} functions can't refer
        to free variables.
  \item 21\% of the students think mutating a variable defined outside
        a lambda can't possibly change the behavior of the lambda.
  \item Student understanding of the
        \lstinline|let|-over-\lstinline|lambda| pattern is weak.
\end{itemize}
